Efficient spherical Convolutional Neural Networks with Healpix sampling for cosmological applications

### 2018-04-05 scnn.tex
add a plot list

@@

@@

@@

Show the spherical harmonics.

@@

@@

\begin{itemize}
	\item We need efficient convolution, hence the Chebysheff trick
	\item Define spherical CNN using graph CNN
\end{itemize}

@@

@@

>>>>

\todo{Cool to have a global illustration of the network (CNN like)}

@@

Figure Graph (show also the triangle, separate plot?) + sampling

@@

Figure heaplix pooling.

@@

Figure our harmonics.

@@

Example on the heat equation
Figure filters
Figure diffusion (unit of heat)

@@

\begin{itemize}
	\item We need efficient convolution, hence the Chebysheff trick
	\item Explain the different between a polynomial filter convolution and a traditional patch restricted convolution
	\item Define spherical CNN using graph CNN
\end{itemize}

@@

Figure: part map plot

@@

Figure: Result curves

Figure: Filter if they look good.
